---
output: github_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# covidQuarantineViz

covidQuarantineViz is an R package that turns the simulated quarantine
analysis from ETC5523 into a reproducible, interactive workflow.

The package:

1. Bundles three simulation scenarios from Michael Lydeamore's
   COVIDQuarantine model (traveller vs worker, vaccinated vs unvaccinated),

2. Exposes the combined dataset as quarantine_data,

3. Provides a Shiny app to explore differences in incubation times between
   scenarios, and

4. Includes a vignette and documentation website to explain the analysis.

This package was developed as part of ETC5523 Assignment 4: Turning analysis
interactive. It takes the ideas from Assignments 1–3 and wraps them into a
distributable R package with an interactive Shiny component.

## Installation

You can install the development version from GitHub with:

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("ETC5523-2025/assignment-4-packages-and-shiny-apps-DhruvGal")
```

## Getting started

Load the package:
```{r}
library(covidQuarantineViz)
```


## The main dataset: quarantine_data

The core dataset included in the package is quarantine_data, which combines
three simulation outputs from the COVIDQuarantine model into a single data
frame. Each row corresponds to one simulated individual in one scenario.

```{r}
data("quarantine_data", package = "covidQuarantineViz")
head(quarantine_data)
```

Key variables include:

scenario: Simulation scenario (traveller/worker and vaccination status).

group: Whether the scenario relates to travellers or workers.

t_incubation: Simulated incubation time (days) until symptom onset.

Other variables from the original simulation outputs.

For full details, see the help page:

```{r}
?quarantine_data
```

## Launching the Shiny app

The package includes an interactive Shiny app that allows you to explore the
distribution of incubation times by scenario and to compare simple summary
statistics.

Launch the app with:

```{r, eval = FALSE}
run_quarantine_app()
```

In the app you can:

select a scenario (e.g. traveller vs worker, vaccinated vs unvaccinated),

view the incubation time distribution for the selected scenario, and

inspect a summary table (mean, median, min, max, sample size) for
incubation times.

The sidebar describes the key fields, and each tab includes guidance on how to
interpret the plot and the table.

## Vignette

A more detailed walkthrough of the dataset and analysis is provided in the
package vignette. It reproduces simple summaries and plots and explains how the
Shiny app fits into the broader ETC5523 analysis.

You can open the vignette with:
```{r}
vignette("overview", package = "covidQuarantineViz")
```

The vignette:

gives an overview of the quarantine_data structure,

shows example summaries of incubation time by scenario, and

demonstrates simple visualisations that match the story told in the app.

## Package website

A pkgdown website is available for this package, providing function reference
pages and access to the vignette in a web browser:

<https://etc5523-2025.github.io/assignment-4-packages-and-shiny-apps-DhruvGal/>

## Data source and attribution

The quarantine_data dataset is derived from three CSV files in the
COVIDQuarantine GitHub repository by Michael Lydeamore. These simulations
describe quarantine scenarios for travellers and workers in hotel quarantine
over 14 days, under different vaccination assumptions.

This package repackages those simulation outputs for teaching in ETC5523 and
adds an interactive interface to help users explore how the incubation time
distribution changes under different scenarios.

